GHRVis:

### 2022-02-02 paper/section/data.tex
draft: EHR data description

\subsubsection{River Thames}

We first obtained the relation ID (2263653) for River Thames from OpenStreetMap \cite{openstreetmapRelation}, then downloaded the entire shapefile via a query (See Listing~\ref{overpass}) through the Overpass Turbo \cite{overpassturboOverpass}.

\begin{lstlisting}[caption={The Overpass Turbo query that downloads the shapefile of River Thames from OpenStreetMap.}, label={overpass},captionpos=b]
    relation(2263653);>>;
    out skel;
\end{lstlisting}

@@

We obtained the Clinical Commissioning Group Outcomes Indicator Set (CCG OIS) from NHS Digital \cite{nhsdigitalClinical}. The OIS is a set of indicators that are used to measure the quality of care and the associated health outcomes in the NHS.

>>>>

\subsubsection{Rivers}

We used OpenStreetMap \cite{openstreetmapRelation} as our data source to obtain shapefiles for River Thames, River Trent and River Ouse in England. These rivers were chosen as they pass through regions with clusters of CCGs, and provide informative geographical and topological cues.

We first obtained a relation ID for the shapefile from OpenStreetMap, then downloaded the entire shapefile via a query (See Listing~\ref{overpass}) through Overpass Turbo \cite{overpassturboOverpass}.

\begin{lstlisting}[caption={The query that downloads the shapefile of River Thames from OpenStreetMap via Overpass Turbo API.}, label={overpass},captionpos=b]
    relation(2263653);>>;
    out skel;
\end{lstlisting}

@@

We obtained the Clinical Commissioning Group Outcomes Indicator Set (CCG OIS) from NHS Digital \cite{nhsdigitalClinical}. The OIS is a set of indicators that are used to measure the quality of care and the associated health outcomes in the NHS. Some datasets include:
\begin{itemize}
    \item Under 75 mortality
    \begin{multicols}{2}
        \begin{itemize}
            \item Cardiovascular disease
            \item Respiratory disease
            \item Liver disease
            \item Cancer
        \end{itemize}
    \end{multicols}
    \item Emergency hospital admission
        \begin{itemize}
            \item Stoke
            \item Alcohol-specific admission and readmission
            \item Coronary heart disease
            \item Readmissions within 30 days of discharge
            \item Children with lower respiratory tract infections
        \end{itemize}
\end{itemize}

For all datasets, a spreadsheet including the following data is provided:

\begin{itemize}
    \item Reporting period: Calendar year of registration
    \item Period of coverage: Start and end date or reporting period
    \item Breakdown: Organization type
    \item ONS code: UK Office for National Statistics CCG code
    \item Level: CCG Code
    \item Level description: CCG Name
    \item Gender
    \item Indicator value: Directly standardized mortality rate
    \item CI lower: lower 95\% confidence interval
    \item CI upper: upper 95\% confidence interval
    \item Denominator: The count of registered patients
    \item Numerator: Number of deaths
\end{itemize}
